Finding the Most Suitable Code Clone Refactoring Techniques by Mapping Clone Context

### 2019-12-06 cefp/paper.tex
Abstract

We find that most clones (77\%) are in the body of methods or constructors and thus the ``Extract Method'' refactoring technique applies. What further techniques are requires for the refactoring depends on the relation among the clone instances of a clone. We define four relations that require different further refactoring techniques: Common Class, Common Hierarchy, Common Interface, Unrelated. For each of these, we define subcategories to facilitate further understanding in what relations clones are found in the codebase.

>>>>

Based on experiments on corpus of open-source Java projects we find that most clones (77\%) are in the body of methods or constructors and thus the ``Extract Method'' refactoring technique applies. What further techniques are required for the refactoring depends on the relation among the clone instances of a clone. We define four relations that require different further refactoring techniques: Common Class, Common Hierarchy, Common Interface and Unrelated. % (ordered by how favorable their refactoring is). When clones are in the same class, no further techniques than ``Extract Method'' have to be applied. If they are not, further techniques have to be applied that create a trade-off on system maintainability. 
The closer classes are related, the more favorable refactoring clones by such relations becomes. 37\% of clones are in the same class, 24\% share an inheritance hierarchy, 24\% are unrelated and 15\% have a common interface.% For each of these, we define subcategories to facilitate further understanding in what relations clones are found in the codebase.
